---
title: "Billboard"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install/Load Packages
```{r Packages}

#{install.packages("pacman")}  
#library(pacman)

pacman::p_load(tidygraph, igraph, igraphdata, dplyr, billboard, spotifyr, rcrossref, ggplot2, ggraph, tidygraph, tidyverse, readr, tidyr)
```

##Lyrics
```{r}

data(lyrics, package = 'billboard')

if (require("dplyr")) {

  data(lyrics)

  lyrics %>% glimpse()

}


```

## Spotify Playlists
```{r}

data(spotify_playlists, package = 'billboard')

if (require("dplyr")) {

  data(spotify_playlists)

  spotify_playlists %>% glimpse()

}

```

## Spotify Track Data 
```{r}
if (require("dplyr")) {

  data(spotify_track_data)

  spotify_track_data %>% glimpse()

}
```



## This tracks the years that had the most danceable years, taking music from the billboard top 100. 
## By plotting a regression line, it shows that the late 1970's and 1980 hits the peak of the most danceable music era. Danceability then shows to decline into 2015, and predicts to continue in this direction. 
```{r}

toptrack <- spotify_track_data %>%
  group_by(year) %>%
  summarise(danceability = n())

toptrack$year <- as.numeric(as.character(toptrack$year))

ggplot(toptrack, aes(x= year,y= danceability)) + 
  geom_point() + 
  stat_smooth(method = "lm",
              formula = y ~ x + poly(x, 2) - 1) + 
  labs(x = "Year", y = "Danceability")

```


## Taking Daceability into consideration, we can then look at particularly the most danceable songs, and the least danceable songs. 
```{r Dataset, message=FALSE, warning=FALSE}
# Load the enron dataset
dance <- toptrack %>%
  select(year, danceability) %>%
  group_by(year) %>%
  as_tbl_graph() %>%
  activate(nodes) %>%
  mutate(
    deg = centrality_degree()
  )
plot(dance)
```


##Taking Danceability into consideration, we can then look at the specific songs, instead of years that are the most danceable. Comparing these songs to Tempo, one can undestand the mean Tempo that makes a song Danceable.

##By looking at the Graph, the most danceable songs have an average Tempo of 116 beats per minute. 

```{r}
top_dancing_songs <- spotify_track_data %>%
  arrange(desc(danceability)) %>%
  head(10)

pc1 <- ggplot(top_dancing_songs, aes(x = track_name, y = tempo, color = artist_name))
pc1 + geom_point() +
  geom_line()+
  geom_hline(aes(yintercept = mean(tempo))) +
theme(axis.text.x = element_text(angle = 90, hjust = 1))

pc2 <- pc1 +
  geom_smooth(mapping = aes(linetype = "r2"),
              method = "lm",
              formula = y ~ x + log(x), se = FALSE,
              color = "red")

pc2 + geom_point()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

##Looking at the least danceable songs, one may think that the beats per minute might have a huge differing factor, but it appears the beats per minute sit at an average over 125 beats per minute. Looking at the data without taking the mean into consideration, it appears that these songs either have a very low beats per minute count or a very high beats per minute count. The range of this graph goes from below 50 beats per minute to over 200 beats per minute. This differs from the top danceable songs, where the graph's danceablity numbers range from 100 to 120 beats per minute. The majority of the songs also float close to the mean line. This shows that a tempo around 116-120 beats per mintue is the best for a popular dancing song. 
```{r}
bottom_dancing_songs <- spotify_track_data %>%
  arrange(danceability) %>%
  head(10)


pg1 <- ggplot(bottom_dancing_songs, aes(x = track_name, y = tempo, color = artist_name))
pg1 + geom_point() +
  geom_line()+
  geom_hline(aes(yintercept = mean(tempo))) +
theme(axis.text.x = element_text(angle = 90, hjust = 1))

pg2 <- pc1 +
  geom_smooth(mapping = aes(linetype = "r2"),
              method = "lm",
              formula = y ~ x + log(x), se = FALSE,
              color = "red")
pg2 + geom_point()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



