---
title: "Genre-Ratio"
author: "Dream team"
date: "07/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggraph)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tibble)
library(tidygraph)
library(igraph)
library(data.table)
```

# Fetched DATA
```{r}
#colaboration_data <- readRDS(data_in/colaboration_data.rds)
```

The point of this markdown was to see the proportions of genres in the communities we detected for Question 6.

Comments will flow like this: 
1. Create two dataset: one for NODE and one for EDGEs
2. Filter for just one Community 
3. Extract edges that occure JUST in that community
4. Extract the Genres of those edges into list
5. Summarize the genres data into ratios proportional to community size.
6. Put this logic into a loop and do it 100 times 
7. save everything into one dataset -> GenreRatio_DB


# Converted data
convert data to as_tbl_graph
```{r}
colaboration_data_tbl2 <- as_tbl_graph(colaboration_data, directed = FALSE)
```

# 1. Create two dataset: one for NODE and one for EDGEs
Run community detection to assign each node to a community.
```{r}
colab_detect <- colaboration_data_tbl2 %>%
  mutate(comm_detec = group_louvain())

comm_node <- as.data.frame(colab_detect) #node
comm_edg <- colab_detect %>%             #edge
            activate(edges) %>%
            as.data.frame()
```

Add a Matching Row number ID ( to link the two data sets... From# To# ID#)
```{r}
comm_node$ID <- 1:nrow(comm_node) 
```

# 2. Filter for just one Community 
```{r}
# Create empty db
GenreRatio_DB <- data.frame(
                      Com_e = integer(),
                      Freq = character(),
                      Comm = character(),
                      Ratio = integer())
  
for(x in 1:100){
  com_n <- comm_node %>%
    filter(comm_detec == 1)
  
  
# 4 Extract the Genres of those edges into list
  
  Com_e <- NULL
  for( y in 1:nrow(comm_edg)){
      if(comm_edg$to[y] %in% com_n$ID & comm_edg$from[y] %in% com_n$ID == TRUE){
        Com_e <-append(Com_e,comm_edg$genre[y])
      }
  }

# 5 Summarize the genres data into ratios proportional to community size.
  Total <- length(Com_e)
  summary <- as.data.frame(table(Com_e))
  summary$Comm <- x
  Ratio <- NULL
  for(z in 1:length(summary$Freq)){
    ratio2 <- round((summary$Freq[z]/Total),2)
    Ratio <- append(Ratio,ratio2)
  }
  Ratio_COL <- as.data.frame(Ratio)
  summary <- cbind(summary,Ratio_COL)
  GenreRatio_DB<- rbind(GenreRatio_DB,summary)  #7 save everything into one dataset -> GenreRatio_DB
  summary
}
GenreRatio_DB
```


```{r}
GenreRatio_DB <- saveRDS(GenreRatio_DB,"data_out/community_genre_ratio.rds")
```



```
